---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Verdana, sans-serif;
  background-color: #f4f4f4;
    background: linear-gradient(to right, rgba(0, 0, 255, 0.2), rgba(128, 0, 128, 0.6));

  padding: 20px;
}

h2 {
  color: Black;
  text-decoration: underline;
  font-weight: bold;
  text-shadow: 2px 2px 4px rgba(0, 0, 0, 0.5);
  font-size: 24px;
}

h1, h3 {
  font-family: 'Verdana', sans-serif;
  color: #333;
}

h1 {
  font-size: 28px;
  font-weight: bold;
}

h3 {
  font-size: 20px;
  font-weight: normal;
}

.ggplot-container {
  border: 2px solid #ccc;
  padding: 20px;
  background-color: #ffffff;
  margin-top: 20px;
  margin-bottom: 20px;
  border-radius: 8px;
}

table {
  width: 100%;
  border-collapse: collapse;
}

table, th, td {
  border: 1px solid #ddd;
}

th, td {
  padding: 8px;
  text-align: left;
}

th {
  background-color: #f2f2f2;
}

/* Adding a border specifically around the bar charts */
div.figure {
  border: 3px solid #3498db; /* Blue border for the charts */
  padding: 15px;
  margin: 15px;
  border-radius: 10px;
}

```

## Internet Ads Tracking Log

This report analyzes an Internet Ads Tracking Log that looks into received ads over a two-week period. This includes 

- **Perceived Relevance**: A bar chart displaying how relevant the Ads were to me.  
- **Platforms**: A bar chart displaying platforms and social media where I received the ads from. 
- **Ads types**: A bar chart displaying the different types of ads I received  
- **Ad Frequency**: A bar chart displaying how many times a day I got the ads


```{r}
library(magick)
library(tidyverse)

# Read the data 
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRVaAg3eQdeYMgzQM3Tc2A3Rs3QHk4tiAqwwVWZg8C8NthHya7V6hCfybleXdUJrUqch8b3T70r2YLH/pub?output=csv")

# Rename variables 
latest_data <- logged_data %>%
  rename(
    product_type = "What type of product or service was being advertised?",
    ad_frequency = "In the past 7 days, how many times have you seen ads related to the following topic(s)?",
    platform = "Which platform did you see the ad on?",
    relevance = "How relevant do you think these ads are to your personal interests?"
  )

# Create a frequency table for product types
product_counts <- latest_data %>%
  separate_rows(product_type, sep = ", ") %>%
  count(product_type) %>%
  arrange(desc(n))

# Create a frequency table for platforms
platform_counts <- latest_data %>%
  separate_rows(platform, sep = ", ") %>%
  count(platform) %>%
  arrange(desc(n))

# Most common product type advertised
most_common_product <- product_counts %>%
  slice(1) %>%
  pull(product_type)

# Percentage of ads that were very relevant
very_relevant_pct <- latest_data %>%
  summarise(pct = mean(relevance == "Very relevant") * 100) %>%
  pull(pct) %>%
  round(1)

# Bar chart 1: Frequency of different product types
ggplot(product_counts, aes(x = reorder(product_type, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Frequency of Different Advertised Product Types",
    x = "Product Type",
    y = "Count"
  ) +
  theme_minimal()

# Get the max and min for product counts
product_max_min <- product_counts %>%
  summarise(
    max_count = max(n),
    min_count = min(n)
  )



# Dynamic comment for product types
product_comment <- paste("The most advertised product type is '", most_common_product, 
                         "' with a count of ", product_max_min$max_count, ".",
                         " The least advertised product type has a count of ", product_max_min$min_count, ".", sep = "")
print(product_comment)

# Bar chart 2: Distribution of ad relevance
ggplot(latest_data, aes(x = relevance)) +
  geom_bar(fill = "coral") +
  labs(
    title = "Distribution of Ad Relevance to Personal Interests",
    x = "Perceived Relevance",
    y = "Count"
  ) +
  theme_minimal()

# Get the max and min for relevance counts
relevance_max_min <- latest_data %>%
  count(relevance) %>%
  summarise(
    max_count = max(n),
    min_count = min(n)
  )

# Dynamic comment for ad relevance
relevance_comment <- paste("The highest number of responses rated ads as 'Very relevant', with a total count of ",
                           relevance_max_min$max_count, ". The lowest response count is ", relevance_max_min$min_count, ".", sep = "")
print(relevance_comment)

# Bar chart 3: Ad frequency distribution
ggplot(latest_data, aes(x = ad_frequency)) +
  geom_bar(fill = "darkgreen") +
  labs(
    title = "Distribution of Ad Frequency in Past 2 weeks",
    x = "Frequency Range",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Get the max and min for ad frequency counts
ad_frequency_max_min <- latest_data %>%
  count(ad_frequency) %>%
  summarise(
    max_count = max(n),
    min_count = min(n)
  )

# Dynamic comment for ad frequency
ad_frequency_comment <- paste("The highest frequency of ads seen was ", ad_frequency_max_min$max_count, 
                              " times, while the lowest was ", ad_frequency_max_min$min_count, ".", sep = "")
print(ad_frequency_comment)

# Bar chart 4: Platform distribution
ggplot(platform_counts, aes(x = reorder(platform, n), y = n)) +
  geom_col(fill = "purple") +
  coord_flip() +
  labs(
    title = "Frequency of Platforms Where Ads Were Seen",
    x = "Platform",
    y = "Count"
  ) +
  theme_minimal()

# Get the max and min for platform counts
platform_max_min <- platform_counts %>%
  summarise(
    max_count = max(n),
    min_count = min(n)
  )

# Dynamic comment for platform distribution
platform_comment <- paste("The platform with the highest frequency of ads was '", 
                          platform_counts$platform[which.max(platform_counts$n)], 
                          "' with a count of ", platform_max_min$max_count, ".", 
                          " The platform with the lowest ad count had ", platform_max_min$min_count, ".", sep = "")
print(platform_comment)


```

